### 2023-11-06 main.tex
^^

This notation is equivalent to the one introduced. Indeed, assume that at site $x$ we have a particle of type $a\in\{1,\ldots,N\} $, then $|n^{x}\rangle$ is composed by zeros but in the component $n_{a}^{x}$ where there is $1$. Therefore, we can uniquely associate  $\tau_{x}=a$ to this $|n^{x}\rangle$, denoting the presence of the species $a$ at site $x$. With this notation, we have that 
\begin{equation}\label{notation}
	|n^{x}\rangle =|\tau_{x}\rangle \qquad \text{and}\qquad|\bm{n}\rangle=|\bm{\tau}\rangle
with the meaning explained above. It will be useful to introduce also $\bm{\tau}=(\tau_{x})_{x\in \{1,\ldots,L\}}$.
We state the following result: the ground state of the Hamiltonian $H^{''}$ is given by 
\begin{equation}\label{ResulsBasis}
	|\Psi^{''} \rangle= \sum_{\tau}\frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} \lambda_{\tau_{x}}^{(1-\delta_{\tau_{x},N})}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right) |\tau\rangle
%\begin{equation}\label{ResulsBasis}
%	|\Psi^{''} \rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}\left(\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\right]^{1-\delta_{\tau_{x},N}}\right)|\mathbf{\bm{\tau}}\rangle
    \delta_{\tau_{x},N}:=\begin{cases}
        N\quad \text{if}\quad \tau_{x}=N\\
        0\quad \text{otherwise}
\textbf{Remark}: In case of $N=2$ we introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$. Moreover, for each $q\in \{1,\ldots,L\}$ we call $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$ the coordinates where particles of type $1$ are present. Thus, the coefficient of the above formula can be written as

@@

In the first part of the proof we will use the notation with $\bm{n}$, then we will change to the notation with $\bm{\tau}$ at the end of the proof. We recall that these two notations are related by \eqref{notation-change-relation}.  We consider the vector with elements given by the operators of the MPA $(X_{1},\ldots,X_{N})$ and we act on it with the similarity transformation $S=S_{2}S_{1}$ obtaining new operators $(\Xt_{1},\ldots,\Xt_{N})$ that will satisfy simpler commutation relations. 

@@

with $\widetilde{X}_{N}=\widetilde{X}_{1}+\ldots+\widetilde{X}_{1}$, see \eqref{Xtildes2b}. 

@@

	|\Psi^{''}\rangle = \frac{1}{Z_{L}}\sum_{\bm{n}\in \Omega}\langle V^{*}|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
	|V \rangle \,|\bm{n}\rangle

@@

To determine the steady state \eqref{toDetermineTilde}, we need to compute the coefficient $\langle V^{*}|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{\xi_{a}^{x}}

@@

	\widetilde{X}_{1}^{\ell}\left(\widetilde{X}_{a}+\ell\lambda_{a}\right)^{n}

@@

	\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}=\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\widetilde{X}_{a}+\lambda_{a}\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}\dt

@@

	\langle V^{*}|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
	|V \rangle\nonumber&=\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}+\lambda_{a}\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|V\rangle\nonumber
	\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|V\rangle\nonumber
	\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}|V\rangle \dt
To determine the state we now need to compute $\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}|V\rangle$. Calling $\sum_{i=1}^{L}n_{N}^{i}=n_{N}$ and using \eqref{commLEFT} for $a\in \{1,\ldots,N-1\}$ we obtain 

@@

	\langle V^{*}|\widetilde{X}_{N}^{n_{N}}|V\rangle&=\langle V^{*}|\widetilde{X}_{N}\widetilde{X}_{N}^{n_{N}-1}|V\rangle=\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}|V\rangle +\langle V^{*}|\frac{1}{\lambda_{a}}\widetilde{X}_{a}\widetilde{X}_{N}^{n_{N}-1}|V\rangle
	\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}|V\rangle+\frac{1}{\lambda_{a}}\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}\left(\widetilde{X}_{a}+\lambda_{a}(n_{N}-1)\right)|V\rangle
	\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}|V\rangle+\left(n_{N}+1-1\right)\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}|V\rangle
	\left(2+n_{N}-1\right)\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}|V\rangle
	\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\langle V^{*}|\widetilde{X}_{N}^{n_{1}-1}|V\rangle

@@

		\langle V^{*}|\widetilde{X}_{N}^{n_{N}}|V\rangle=\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}|V\rangle

@@

	\langle V^{*}|\widetilde{X}_{N}^{n_{N}}|V\rangle&=%\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}|V\rangle=\langle V^{*}|\widetilde{X}_{N}^{n_{N}}|V\rangle=\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\frac{\Gamma(2+n_{N}-1)}{\Gamma(2+n_{N}-2)}\langle V^{*}|\widetilde{X}_{N}^{n_{N}-2}|V\rangle\\&=
	\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\frac{\Gamma(2+n_{N}-1)}{\Gamma(2+n_{N}-2)}\ldots \frac{\Gamma(2-1)}{\Gamma(2)}\langle V^{*}|\widetilde{X}_{N}^{0}|V\rangle=
	\Gamma(2+n_{N})

@@

By using this result we have 
	\langle V^{*}|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
	|V \rangle=\Gamma(2+n_{N})\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}
The normalization constant is computed similarly as 

@@

	Z_{L}&=\langle V^{*}|(X_{1}+\ldots+X_{N})^{L}|V\rangle=\langle V^{*}\widetilde{X}_{N}^{L}|V|\rangle=

@@

	|\Psi^{''}\rangle= \sum_{\bm{n}\in \Omega}\frac{\Gamma(2+\sum_{i=1}^{L}n_{N}^{i})}{\Gamma(2+L)}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|\bm{n}\rangle\dt

@@

The last factor only depends on the positions of particles $N$. The $\lambda$-factor depends only on the number of particles of types $1,\ldots,N-1$.

@@

@@

    |\Psi^{'}\rangle =\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\Psi^{'}(\bm{\tau})|\bm{\tau}\rangle 

>>>>

This notation is equivalent to the one introduced. Indeed, assume that at site $x$ we have a particle of type $a\in\{1,\ldots,N\} $, then $|n^{x}\rangle$ is composed by zeros but in the component $n_{a}^{x}$ where there is $1$. Therefore, we can uniquely associate  $\tau_{x}=a$ to this $|n^{x}\rangle$, denoting the presence of the species $a$ at site $x$. With this notation, we have that 
\begin{equation}\label{notation}
	|n^{x}\rangle =|\tau_{x}\rangle \qquad \text{and}\qquad|\bm{n}\rangle=|\bm{\tau}\rangle
\end{equation}
with the meaning explained above. It will be useful to introduce also $\bm{\tau}=(\tau_{x})_{x\in \{1,\ldots,L\}}$.
\end{comment} 
We state the following result: the ground state of the Hamiltonian $H^{''}$ is given by 
\begin{equation}\label{ResulsBasis}
	|\Psi^{''} \rangle= \sum_{\bm{\tau}\in \Omega}\frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} \lambda_{\tau_{x}}^{(1-\delta_{\tau_{x},N})}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right) |\bm{\tau}\rangle
\end{equation}
%\begin{equation}\label{ResulsBasis}
%	|\Psi^{''} \rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}\left(\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\right]^{1-\delta_{\tau_{x},N}}\right)|\mathbf{\bm{\tau}}\rangle
%\end{equation}
where 
\begin{equation}
    \delta_{\tau_{x},N}:=\begin{cases}
        N\quad \text{if}\quad \tau_{x}=N\\
        0\quad \text{otherwise}
    \end{cases}
\end{equation}

@@

%In the first part of the proof we will use the notation with $\bm{n}$, then we will change to the notation with $\bm{\tau}$ at the end of the proof. We recall that these two notations are related by \eqref{notation-change-relation}.  
We consider the vector with elements given by the operators of the MPA $(X_{1},\ldots,X_{N})$ and we act on it with the similarity transformation $S=S_{2}S_{1}$ obtaining new operators $(\Xt_{1},\ldots,\Xt_{N})$ that will satisfy simpler commutation relations. 

@@

with $\widetilde{X}_{N}=\widetilde{X}_{1}+\ldots+\widetilde{X}_{N}$, see \eqref{Xtildes2b}. 

@@

	|\Psi^{''}\rangle = \frac{1}{Z_{L}}\sum_{\bm{\tau}\in \Omega}\langle V^{*}|\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
	|V \rangle \,|\bm{\tau}\rangle

@@

To determine the eigenvector \eqref{toDetermineTilde}, we need to compute the coefficient $\langle V^{*}|\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}

@@

	\widetilde{X}_{N}^{\ell}\left(\widetilde{X}_{a}+\ell\lambda_{a}\right)^{n}

@@

	\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}=\widetilde{X}_{N}^{\sum_{x=1}^{L}\delta_{\tau_{x},N}}\prod_{x=1}^{L}\left(\widetilde{X}_{\tau_{x}}+\lambda_{\tau_{x}}\sum_{j=x}^{L}\delta_{\tau_{x},N}\right)^{n_{a}^{x}}\dt

@@

	\langle V^{*}|\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
	|V \rangle\nonumber&=
	\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}\langle V^{*}|\widetilde{X}_{N}^{\sum_{x=1}^{L}\delta_{\tau_{x},N}}|V\rangle \dt
We now need to compute $\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}\delta_{\tau_{x},N}}|V\rangle$. For all $n\in \mathbb{N}$ we have that  

@@

	\langle V^{*}|\widetilde{X}_{N}^{n_{N}}|V\rangle&=\langle V^{*}|\widetilde{X}_{N}\widetilde{X}_{N}^{n-1}|V\rangle=\langle V^{*}|\widetilde{X}_{N}^{n-1}|V\rangle +\langle V^{*}|\frac{1}{\lambda_{a}}\widetilde{X}_{a}\widetilde{X}_{N}^{n-1}|V\rangle
	\langle V^{*}|\widetilde{X}_{N}^{n-1}|V\rangle+\frac{1}{\lambda_{a}}\langle V^{*}|\widetilde{X}_{N}^{n-1}\left(\widetilde{X}_{a}+\lambda_{a}(n-1)\right)|V\rangle
	\langle V^{*}|\widetilde{X}_{N}^{n-1}|V\rangle+\left(n+1-1\right)\langle V^{*}|\widetilde{X}_{N}^{n-1}|V\rangle
	\left(2+n-1\right)\langle V^{*}|\widetilde{X}_{N}^{n-1}|V\rangle
	\frac{\Gamma(2+n)}{\Gamma(2+n-1)}\langle V^{*}|\widetilde{X}_{N}^{n-1}|V\rangle

@@

		\langle V^{*}|\widetilde{X}_{N}^{n}|V\rangle=\frac{\Gamma(2+n)}{\Gamma(2+n-1)}\langle V^{*}|\widetilde{X}_{N}^{n-1}|V\rangle

@@

	\langle V^{*}|\widetilde{X}_{N}^{n}|V\rangle&=%\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}|V\rangle=\langle V^{*}|\widetilde{X}_{N}^{n_{N}}|V\rangle=\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\frac{\Gamma(2+n_{N}-1)}{\Gamma(2+n_{N}-2)}\langle V^{*}|\widetilde{X}_{N}^{n_{N}-2}|V\rangle\\&=
	\frac{\Gamma(2+n)}{\Gamma(2+n-1)}\frac{\Gamma(2+n-1)}{\Gamma(2+n-2)}\ldots \frac{\Gamma(2-1)}{\Gamma(2)}\langle V^{*}|\widetilde{X}_{N}^{0}|V\rangle=
	\Gamma(2+n)

@@

By using this result we have that
	\langle V^{*}|\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}
	|V \rangle=\Gamma(2+\sum_{x=1}^{N}\delta_{\tau_{x},N})\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}
The normalization constant is then given by

@@

	Z_{L}&=\langle V^{*}|(X_{1}+\ldots+X_{N})^{L}|V\rangle=\langle V^{*}|\widetilde{X}_{N}^{L}|V|\rangle=

@@

	|\Psi^{''}\rangle= \sum_{\bm{\tau}\in \Omega}\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(2+L)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}|\bm{\tau}\rangle\dt
We observe that, for all $x$, we have
	\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}=\frac{\Gamma(2+\sum_{j=x+1}^{L}\delta_{\tau_{j},N})}{\Gamma(1+\sum_{j=x}\delta_{\tau_{j},N})}

@@

It follows that 
\begin{align}\label{remove-exponent}
&\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(2+L)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\right)^{1-\delta_{\tau_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)^{1-\delta_{\tau_{x},N}}\nonumber\\
=&\frac{\Gamma(2+\sum_{x=1}^{L}\delta_{\tau_{x},N})}{\Gamma(2+L)}\prod_{x=1}^{L}\frac{\Gamma(2+\sum_{j=x+1}^{L}\delta_{\tau_{j},N})}{\Gamma(1+\sum_{j=x}\delta_{\tau_{j},N})}\nonumber\\
=&\frac{\Gamma(2)}{\Gamma(2+L)}\prod_{x=1}^{L}\frac{\Gamma(2+\sum_{j=x}^{L}\delta_{\tau_{j},x})}{\Gamma(1+\sum_{j=x}^{L}\delta_{\tau_{j},x})}\nonumber\\
=&\frac{1}{(1+L)!}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)
Therefore, we obtain \eqref{ResulsBasis}.
%The last factor only depends on the positions of particles $N$. The $\lambda$-factor depends only on the number of particles of types $1,\ldots,N-1$.

@@

\textbf{Remark}: In case of $N=2$ we introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$. Moreover, for each $q\in \{1,\ldots,L\}$ we call $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$ the coordinates where particles of type $1$ are present. Thus, arguing as in \eqref{remove-exponent}, the coefficient \eqref{ResulsBasis} when $N=2$ are written as

@@

    |\Psi^{'}\rangle =\sum_{\bm{\tau}\in \Omega}\Psi^{'}(\bm{\tau})|\bm{\tau}\rangle 
